Use cases that describe functionality of the chatroom pool seen on the administrative side.

%--------------------------------------------------------------------------------------
\UseCaseNew{Receive Chatroom}{receive_chatroom}{%
     Describes the process when a User receives a chatroom.
}{%
    \FakeItem User
}{%
    \FakeItem The User has the property authority.
}{%
    \FakeItem \textit{Implicit}
}{%
    \FakeNumberedItem{1} The chatroom pool page is updated on the display. \par
    \FakeNumberedItem{2} A notification is sent to the User at 0, 60, 90, 120, etc. seconds.
}{%
    The chatroom pool page has been updated.
}
%--------------------------------------------------------------------------------------
\UseCaseNew{Set User Activity Status}{set_user_status}{%
     Describes the process when a User sets their activity status
}{%
    \FakeItem User
}{%
    \FakeItem The User has the proper authority.
}{%
    \FakeItem The User requests to change their activity status.
}{%
    \FakeNumberedItem{1} The User requests to change their activity status. \par
    \FakeNumberedItem{2} The User's activity status is changed and the display is updated.
}{%
    The User's activity status is updated accordingly.
}
%-------------------------------------------------------------------------------------
\UseCaseNew{Set Away Status}{set_away_status}{%
     Describes the process when a User has their status set to Away.
}{%
    \FakeItem User
}{%
    \FakeItem The User has the proper authority. \par
    \FakeItem The User has had no activity in the application for 10 minutes.
}{%
    \FakeItem The User has exceeded 10 minutes of inactivity.
}{%
    \FakeNumberedItem{1} The User has been inactive for 10 minutes. \par
    \FakeNumberedItem{2} The User's activity status is set to Away and the display is updated.
}{%
    The User's activity status is set to Away.
}
%-------------------------------------------------------------------------------------