This section offers use cases that usually start with the Client on the "Contact Us" page.


%--------------------------------------------------------------------------------------
\UseCaseNew{Visit Library Hours Page}{visit_library_hours_page}{%
    Describes the process when a User acquires the library's operating hours.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests the library's operating hours.
}{%
    \FakeNumberedItem{1} The User navigates to the library's operating hours link. \par
    \FakeNumberedItem{2} The User is redirected to the library's operating hours.
}{%
    The library hours are displayed to the User.
}
%-------------------------------------------------------------------------------------
\UseCaseNew{Visit News \& Events Page}{visit_news_and_events_page}{%
    Describes the process when a User acquires the library's current news and upcoming events.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests information about news \& events.
}{%
    \FakeNumberedItem{1} The User navigates to the library's news \& events link.\par
    \FakeNumberedItem{2} The User is redirected to the library's news \& events page.
}{%
    The news \& events are displayed to the User.
}
%--------------------------------------------------------------------------------------
\UseCaseNew{Visit Tech Suite Booking page}{visit_tech_suite_booking_page}{%
    Describes the process when a User views Tech Suite Booking information.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests information about Tech Suite Booking.
}{%
    \FakeNumberedItem{1} The User navigates to the Tech Suite Booking link. \par
    \FakeNumberedItem{2} The User is redirected to the Tech Suite Booking page.
}{%
    Tech Suite Booking information is displayed to the User.
}
%-------------------------------------------------------------------------------------
\UseCaseNew{Visit Alumni Information Page}{visit_alumni_information_page}{%
    Describes the process when a User views information regarding Alumnae.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests information about Alumni.
}{%
    \FakeNumberedItem{1} The User navigates to the Alumni Information link. \par
    \FakeNumberedItem{2} The User is redirected to the Alumni Information page.
}{%
    Alumni information is displayed to the User.
}
%-------------------------------------------------------------------------------------
\UseCaseNew{Visit FAQs Page}{visit_faqs_page}{%
     Describes the process when a User views the answers to questions commonly asked.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests answers to frequently asked questions.
}{%
    \FakeNumberedItem{1} The User navigates to the Frequently Asked Questions link. \par
    \FakeNumberedItem{2} The User is redirected to the Frequently Asked Questions page.
}{%
    Frequently asked questions and their answers are displayed to the User.
}
%------------------------------------------------------------------------------------
\UseCaseNew{Visit Research A Topic Page}{visit_research_a_topic_page}{%
    Describes the process when a User acquires assistance with researching a topic.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests information about researching a topic.
}{%
    \FakeNumberedItem{1} The User navigates to the Research A Topic link. \par
    \FakeNumberedItem{2} The User is redirected to the Research A Topic Page.
}{%
    Researching a topic information is displayed to the User.
}
%------------------------------------------------------------------------------------
\UseCaseNew{Visit Library Chat}{visit_library_chat}{%
    Describes the process when a User acquires assistance from a librarian.
}{%
    \FakeItem User
}{%
    \FakeItem The User is on the Contact Us page.
}{%
    \FakeItem The User requests to chat with a librarian. 
}{%
    \FakeNumberedItem{1} The User navigates to the Chat With A Librarian link. \par
    \FakeNumberedItem{2} The User is redirected to the Question Specification page. \par
    \FakeNumberedItem{3} The User navigates to the Create Chatroom link. \par
    \FakeNumberedItem{4} The User is paired with a librarian.
}{%
    A librarian joins the User's chatroom to help and answer the User's question.
}
%------------------------------------------------------------------------------------

